---
title: "Ghana Agricultural Profit"
author: "Group 6"
date: "December 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
#Assumptions:
  1. Farms bigger than 0.2 Acres (including) - 16 Observarions / 0.55%
  2. Farms smaller than 150 Acres (Excluding) - 10 Observarions / 0.34%
  3. profit_per_acre inside 97.5% of confidence interval - 62 observations / 2.1%
  4. Perdiction of LN of profit_per_acre after scale up by the min obervation + 10,000
  5. Exclusion of Communities where Fishing is the main activity

#Descriptive Analysis of Variable

```{r, echo=FALSE}
source("main.R")
base %>% 
  select(-starts_with("region"),
                -starts_with("ez"),
                -starts_with("loc"),
                -ID,
                -nh,
                -farmer) %>% 
  summary()
  
```

##General Model

```{r general_model, echo=FALSE}
mod_9_log <- lm(profit_per_acre_log~most_impor_farming +  moto_road +
                  moto_road_impassable +  have_bar + have_post_of_pub_telephone + have_bank +
                  have_daily_mkt + have_week_mkt + public_transp + people_come_for_job_farming +
                  have_hospital + have_agric_ext_center + have_cooperative + any_farm_use_fert +
                  any_farm_use_inset_herb + any_farm_use_irrigate + mutual_aid_farm +
                  farm_size+I(farm_size^2)+agey+spouse_live_hh+sex_male+fishing+own_business+
                  educ_bece+educ_advanced+
                  region_Western+region_Central+region_Greater_Accra+
                  region_Eastern+region_Volta+region_Ashanti+region_Brong_Ahafo+
                  region_Northern+region_Upper_East+light_eletricity+light_generator+
                  cooking_full_gas+
                  toilet_flush+toilet_latrine+wall_mud+wall_wood+wall_iron+
                  wall_stone+harvest_sold_gate+harvest_sold_market+
                  harvest_sold_consumer+harvest_sold_state_org+harvest_sold_coop+
                  paid_at_sale+paid_at_week+paid_at_month+males_on_farme+
                  females_on_farme, data=base)
summary(mod_9_log)

```

#Standardised residuals plot

```{r, echo=FALSE}
base <- base %>% 
  mutate(
    stand_res = rstandard(mod_9_log)
  )
base %>% ggplot(aes(x = stand_res)) +
  geom_histogram(binwidth = 0.25) + xlab("Standardized residuals")
```

#Residual versus the fitted value
```{r, echo=FALSE}
base$fitted <- mod_9_log$fitted.values
base$residuals <- mod_9_log$residuals
base %>% ggplot(aes(x = fitted, y = residuals)) +
  geom_point()
```

#Is expected that the same factor have different influence in a small, normal or large farm

##1. Model for a small farm (less than 2 Acres - 496 Observations)
```{r, echo=FALSE}
base_small_farms <- base %>% filter(farm_size<2)

mod_9_log <- lm(profit_per_acre_log~most_impor_farming + most_impor_fishing +  moto_road +
                  moto_road_impassable +  have_bar + have_post_of_pub_telephone + have_bank +
                  have_daily_mkt + have_week_mkt + public_transp + people_come_for_job_farming +
                  have_hospital + have_agric_ext_center + have_cooperative + any_farm_use_fert +
                  any_farm_use_inset_herb + any_farm_use_irrigate + mutual_aid_farm +
                  farm_size+I(farm_size^2)+agey+I(agey^2)+spouse_live_hh+sex_male+fishing+own_business+
                  educ_bece+educ_advanced+
                  region_Western+region_Central+region_Greater_Accra+
                  region_Eastern+region_Volta+region_Ashanti+region_Brong_Ahafo+
                  region_Northern+region_Upper_East+light_eletricity+light_generator+
                  cooking_full_gas+
                  toilet_flush+toilet_latrine+wall_mud+wall_wood+wall_iron+
                  wall_stone+wall_cement+harvest_sold_gate+harvest_sold_market+
                  harvest_sold_consumer+harvest_sold_state_org+harvest_sold_coop+
                  paid_at_sale+paid_at_week+paid_at_month+males_on_farme+
                  females_on_farme, data=base_small_farms)
summary(mod_9_log)
```

#Standardised residuals plot Small Farms Model

```{r, echo=FALSE}
base_small_farms <- base_small_farms %>% 
  mutate(
    stand_res = rstandard(mod_9_log)
  )
base_small_farms %>% ggplot(aes(x = stand_res)) +
  geom_histogram(binwidth = 0.25) + xlab("Standardized residuals")
```

#Residual versus the fitted value plot Small Farms Model
```{r, echo=FALSE}
base_small_farms$fitted <- mod_9_log$fitted.values
base_small_farms$residuals <- mod_9_log$residuals
base_small_farms %>% ggplot(aes(x = fitted, y = residuals)) +
  geom_point() 
```

##2. Model for a "Normal" farm (more than 2 Acres(including) and less than 10 (including) - 1787 Observations)
```{r, echo=FALSE}
base_normal_farms <- base %>% filter(farm_size>=2 & farm_size<=10)

mod_9_log <- lm(profit_per_acre_log~most_impor_farming + most_impor_fishing +  moto_road +
                  moto_road_impassable +  have_bar + have_post_of_pub_telephone + have_bank +
                  have_daily_mkt + have_week_mkt + public_transp + people_come_for_job_farming +
                  have_hospital + have_agric_ext_center + have_cooperative + any_farm_use_fert +
                  any_farm_use_inset_herb + any_farm_use_irrigate + mutual_aid_farm +
                  farm_size+I(farm_size^2)+agey+I(agey^2)+spouse_live_hh+sex_male+fishing+own_business+
                  educ_bece+educ_advanced+
                  region_Western+region_Central+region_Greater_Accra+
                  region_Eastern+region_Volta+region_Ashanti+region_Brong_Ahafo+
                  region_Northern+region_Upper_East+light_eletricity+light_generator+
                  cooking_full_gas+
                  toilet_flush+toilet_latrine+wall_mud+wall_wood+wall_iron+
                  wall_stone+wall_cement+harvest_sold_gate+harvest_sold_market+
                  harvest_sold_consumer+harvest_sold_state_org+harvest_sold_coop+
                  paid_at_sale+paid_at_week+paid_at_month+males_on_farme+
                  females_on_farme, data=base_normal_farms)
summary(mod_9_log)
```

#Standardised residuals plot "Normal" Farms Model

```{r, echo=FALSE}
base_normal_farms <- base_normal_farms %>% 
  mutate(
    stand_res = rstandard(mod_9_log)
  )
base_normal_farms %>% ggplot(aes(x = stand_res)) +
  geom_histogram(binwidth = 0.25) + xlab("Standardized residuals")
```

#Residual versus the fitted value plot "Normal" Farms Model
```{r, echo=FALSE}
base_normal_farms$fitted <- mod_9_log$fitted.values
base_normal_farms$residuals <- mod_9_log$residuals
base_normal_farms %>% ggplot(aes(x = fitted, y = residuals)) +
  geom_point() 
```


##3. Model for a Large farm (more than 10 Acres (excluding) - 496 Observations)
```{r, echo=FALSE}
base_large_farms <- base %>% filter(farm_size>10)

mod_9_log <- lm(profit_per_acre_log~most_impor_farming + most_impor_fishing +  moto_road +
                  moto_road_impassable +  have_bar + have_post_of_pub_telephone + have_bank +
                  have_daily_mkt + have_week_mkt + public_transp + people_come_for_job_farming +
                  have_hospital + have_agric_ext_center + have_cooperative + any_farm_use_fert +
                  any_farm_use_inset_herb + any_farm_use_irrigate + mutual_aid_farm +
                  farm_size+I(farm_size^2)+agey+I(agey^2)+spouse_live_hh+sex_male+fishing+own_business+
                  educ_bece+educ_advanced+
                  region_Western+region_Central+region_Greater_Accra+
                  region_Eastern+region_Volta+region_Ashanti+region_Brong_Ahafo+
                  region_Northern+region_Upper_East+light_eletricity+light_generator+
                  cooking_full_gas+
                  toilet_flush+toilet_latrine+wall_mud+wall_wood+wall_iron+
                  wall_stone+wall_cement+harvest_sold_gate+harvest_sold_market+
                  harvest_sold_consumer+harvest_sold_state_org+harvest_sold_coop+
                  paid_at_sale+paid_at_week+paid_at_month+males_on_farme+
                  females_on_farme, data=base_large_farms)
summary(mod_9_log)
```

#Standardised residuals plot Large Farms Model

```{r, echo=FALSE}
base_large_farms <- base_large_farms %>% 
  mutate(
    stand_res = rstandard(mod_9_log)
  )
base_large_farms %>% ggplot(aes(x = stand_res)) +
  geom_histogram(binwidth = 0.25) + xlab("Standardized residuals")
```

#Residual versus the fitted value plot Large Farms Model
```{r, echo=FALSE}
base_large_farms$fitted <- mod_9_log$fitted.values
base_large_farms$residuals <- mod_9_log$residuals
base_large_farms %>% ggplot(aes(x = fitted, y = residuals)) +
  geom_point() 
```
